Topic Scores

### 2019-02-19 Topic Scores.Rmd
simplify code

#
##key word Contributions to Topic
 kw_to_topics <- beta_description$k35                                 %>%
  filter(term %in% student$kw_policy)                                 %>%
  arrange(topic, desc(beta))                                          %>%
  spread(key=topic, value=beta)                                       %>%
  mutate_at(.vars = vars(num_range("Topic ",1:35)),
            .funs = standardize)                                      %>%
   gather(key = "topic", value = "beta_rank", num_range("Topic ", 1:35))
```

>>>>

#
##key word Contributions to Topic
 kw_to_topics <- beta_description$k35                                 %>%
  filter(term %in% student$kw_policy)                                 %>%
  arrange(topic, desc(beta))                                          %>%
  group_by(topic)                                                     %>%
  mutate(beta_sum=sum(beta),
         beta_rank=beta/beta_sum)                                     %>%
  select(-beta_sum, -beta)
```
